{\bf Demystifying Debugging}

### 2012-11-08 gpi-debug/debugging.tex
fix the accidentally correct code to be wrong

	\linegap
		\texttt{~~~~insert\_sorted(list,~element)~\{} \\
			\texttt{~~~~~~~~\hilight{olivegreen}{int}~i~=~\hilight{brickred}{0};} \\
		\texttt{~~~~~~~~\hilight{brown}{while}~(i~<~length(list))~\{} \\
		\texttt{~~~~~~~~~~~~\hilight{brown}{if}~(element~<~list[i])~\{} \\
		\texttt{~~~~~~~~~~~~~~~~\hilight{brown}{break};} \\
		\texttt{~~~~~~~~~~~~\}} \\
		\texttt{~~~~~~~~~~~~i = i + 1;} \\
		\texttt{~~~~~~~~\}} \\
		\texttt{~~~~~~~~insert\_at\_index(list,~element,~i);} \\
		\texttt{~~~~\}} \\
	\pause
	\linegap
	\begin{itemize}
		\item Staring at the code until you see it sometimes works, but is a bad habit.
	\end{itemize}
\end{frame}

@@

	\linegap
		\texttt{~~~~insert\_sorted(list,~element)~\{} \\
			\texttt{~~~~~~~~\hilight{olivegreen}{int}~i~=~\hilight{brickred}{0};} \\
		\texttt{~~~~~~~~\hilight{brown}{while}~(i~<~length(list))~\{} \\
		\texttt{~~~~~~~~~~~~\hilight{brown}{if}~(element~<~list[i])~\{} \\
		\texttt{~~~~~~~~~~~~~~~~\hilight{brown}{break};} \\
		\texttt{~~~~~~~~~~~~\}} \\
		\texttt{~~~~~~~~~~~~i = i + 1;} \\
		\texttt{~~~~~~~~\}} \\
		\texttt{~~~~~~~~insert\_at\_index(list,~element,~i);} \\
		\texttt{~~~~\}} \\
\end{frame}
\begin{frame}{\texttt{insert\_sorted}, revisited}
	Now that we know {\em where} and {\em when} the program breaks, let's fix it.
	\begin{itemize}
		\item Raise your hand (don't say anything) when you see what's wrong.
		\item Remember: only fails at the {\em end of the list}.
	\end{itemize}

	\linegap
		\texttt{~~~~insert\_sorted(list,~element)~\{} \\
			\texttt{~~~~~~~~\hilight{olivegreen}{int}~i~=~\hilight{brickred}{0};} \\
			\texttt{~~~~~~~~\hilight{brown}{while}~(\hilight{red}{i~<~length(list)})~\{~\hilight{darkcyan}{//~Should~be~"<="!}} \\
		\texttt{~~~~~~~~~~~~\hilight{brown}{if}~(element~<~list[i])~\{} \\
		\texttt{~~~~~~~~~~~~~~~~\hilight{brown}{break};} \\
		\texttt{~~~~~~~~~~~~\}} \\
		\texttt{~~~~~~~~~~~~i = i + 1;} \\
		\texttt{~~~~~~~~\}} \\
		\texttt{~~~~~~~~insert\_at\_index(list,~element,~i);} \\
		\texttt{~~~~\}} \\
\end{frame}

>>>>

	\linegap
		\texttt{~~~~insert\_sorted(list,~element)~\{} \\
			\texttt{~~~~~~~~\hilight{olivegreen}{int}~i~=~\hilight{brickred}{0};} \\
			\texttt{~~~~~~~~\hilight{brown}{while}~(i~<~length(list)~-~\hilight{brickred}{1})~\{} \\
		\texttt{~~~~~~~~~~~~\hilight{brown}{if}~(element~<~list[i])~\{} \\
		\texttt{~~~~~~~~~~~~~~~~\hilight{brown}{break};} \\
		\texttt{~~~~~~~~~~~~\}} \\
		\texttt{~~~~~~~~~~~~i = i + \hilight{brickred}{1};} \\
		\texttt{~~~~~~~~\}} \\
		\texttt{~~~~~~~~insert\_at\_index(list,~element,~i);} \\
		\texttt{~~~~\}} \\
	\pause
	\linegap
	\begin{itemize}
		\item Staring at the code until you see it sometimes works, but is a bad habit.
	\end{itemize}
\end{frame}

@@

	\linegap
		\texttt{~~~~insert\_sorted(list,~element)~\{} \\
			\texttt{~~~~~~~~\hilight{olivegreen}{int}~i~=~\hilight{brickred}{0};} \\
			\texttt{~~~~~~~~\hilight{brown}{while}~(i~<~length(list)~-~\hilight{brickred}{1})~\{} \\
		\texttt{~~~~~~~~~~~~\hilight{brown}{if}~(element~<~list[i])~\{} \\
		\texttt{~~~~~~~~~~~~~~~~\hilight{brown}{break};} \\
		\texttt{~~~~~~~~~~~~\}} \\
		\texttt{~~~~~~~~~~~~i = i + 1;} \\
		\texttt{~~~~~~~~\}} \\
		\texttt{~~~~~~~~insert\_at\_index(list,~element,~i);} \\
		\texttt{~~~~\}} \\
\end{frame}
\begin{frame}{\texttt{insert\_sorted}, revisited}
	Now that we know {\em where} and {\em when} the program breaks, let's fix it.
	\begin{itemize}
		\item Raise your hand (don't say anything) when you see what's wrong.
		\item Remember: only fails at the {\em end of the list}.
	\end{itemize}

	\linegap
		\texttt{~~~~insert\_sorted(list,~element)~\{} \\
			\texttt{~~~~~~~~\hilight{olivegreen}{int}~i~=~\hilight{brickred}{0};} \\
			\texttt{~~~~~~~~\hilight{brown}{while}~(\hilight{red}{i~<~length(list)~-~1})~\{~\hilight{darkcyan}{//~Should~be~"<="!}} \\
				\texttt{~~~~~~~~~~~~\hilight{brown}{if}~(element~<~list[i])~\{~~~\hilight{darkcyan}{~~~(or~not~"-1")}} \\
		\texttt{~~~~~~~~~~~~~~~~\hilight{brown}{break};} \\
		\texttt{~~~~~~~~~~~~\}} \\
		\texttt{~~~~~~~~~~~~i = i + 1;} \\
		\texttt{~~~~~~~~\}} \\
		\texttt{~~~~~~~~insert\_at\_index(list,~element,~i);} \\
		\texttt{~~~~\}} \\
\end{frame}
